Figures for Paper

### 2021-03-03 paper_figures.Rmd
Update paper_figures.Rmd

---
title: "Figures for Paper"
author: "Anna-Leigh Brown"
date: "06/10/2020"
output: 
    html_document:
        code_folding: hide
        toc: true
        toc_float: true
---

>>>>

---
title: "Figures for Paper"
author: "Anna-Leigh Brown + Matteo Zanovello"
date: "06/10/2020"
output: 
    html_document:
        code_folding: hide
        toc: true
        toc_float: true
---
